%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{\fontsize{25}{15}\selectfont Abhimanyue}{Singh Tanwar}{
{Interested in People, Algorithms, AI and Full Stack Software Development. }\\
\vspace{
\href{mailto:singhabhimanyu186@gmail.com}{singhabhimanyu186@gmail.com} | +852-65719762 | GitHub:\href{https://github.com/abhimanyu891998}{\custombold{abhimanyu891998}} | Linkedin: \href{https://www.linkedin.com/in/abhimanyue-singh-tanwar-30a424130/}{\custombold{abhimanyue}}
}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.35\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Hong Kong}
\descript{BEng in Computer Science \\ (Finance Minor)}
\location{Expected May 2020}
{Highest Slab of HKU Entrance Scholarship (\custombold{125\%}) |}
{Dean's Honors List | }{ Simon KY Lee Hall Award for Academic Achievement.}

\sectionsep

\subsection{MVM School}
\location{Grad. May 2016 |  Chennai, India}
{\textbf{\custombold{97.8\%}} with PCM and CompSc in All India Senior School Certificate Examination }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements}
\custombold{Champion - Microsoft Imagine Hackathon 2018}\\
{Developed a ML based credit scoring platform on a consortium blockchain.}\\
\vspace{1.5 mm}
\custombold{2nd Runner Up - HackUST 2019}\\
{Developed a mobile-app for on-demand staffing for front-line jobs
in 28 hours. Secured third amongst 100
teams in one of the biggest hackathons in
Asia.}\\
\vspace{1.5 mm}
\custombold{Cyberport University Partnership Program 2019}\\
{Developed a software for decentralised
identity verification process helping in
optimising KYC process. Received 
fully-sponsored fintech executive education \\at \textbf{\custombold{Booth School of
Business, Chicago.}}}\\
\vspace{1.5 mm}
\custombold{Laidlaw Scholar 2018}\\
{Amongst top 6 students who were granted
a scholarship worth HKD 46000 for research
internship at \custombold{UCL, London}.}\\
\vspace{1.5 mm}
\custombold{Microsoft Student Partner - 2018}\\
{Worked on \custombold{Azure} platform to build
solutions for increasing the knowledge
about Microsoft products amongst
university students.}
\sectionsep





% \custombold{Top 4 - Code For Good, JP Morgan, Hong Kong}\\
%  {Amongst the top 4 teams for developing an interactive web application for MIND NGO in Hong Kong as a part of 8 Hour Rapid Hackathon.}



% \custombold{Laidlaw Scholar 2018}\\
%  {Amongst top 6 students who were granted a stipend worth \custombold{HKD 46000}  for research internship at UCL, London.}

 
% \custombold{Runner up(Smart Mobility Category) Smart City Hackathon, Hong Kong 2018}\\
%  {Project Movabilityfor optimising allocation of resources for disabled people in HK using the dataset from Rehab Bus Service, Hong Kong.}
%  \sectionsep
 
%  \custombold{Microsoft Student Partner 2018}\\

%  \sectionsep
% \custombold{Simon KY Lee Hall Award for Academic Achievement 2017}\\
%  \sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% \subsection{Graduate}
% Advanced Machine Learning \\
% Open Source Software Engineering \\
% Advanced Interactive Graphics \\
% Compilers + Practicum \\
% Cloud Computing \\
% \sectionsep

% \subsection{Undergraduate}
% Information Retrieval \\
% Operating Systems \\
% Artificial Intelligence + Practicum \\
% Functional Programming \\
% Computer Graphics + Practicum \\
% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
% Unix Tools and Scripting \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Programming Languages:}
C++ \textbullet{}   Javascript \textbullet{} Python \textbullet{} Java  \textbullet{}  Haskell \\
\vspace{1 mm}
\location{Web Development and Databases:}
React(js/native) \textbullet{}   Node.JS  \textbullet{} MongoDB \textbullet{} SQL  \textbullet{}  Express \textbullet{}  Django \textbullet{}  HTML5 \textbullet{}  CSS\\
\vspace{1 mm}
\location{Tools:}
Git \textbullet{}   Firebase \textbullet{} Azure \textbullet{} Unity  \\
\vspace{1 mm}
\location{Machine Learning:}
Scikit Learn \textbullet{} Pytorch \textbullet{} Tensorflow 

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.64\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{JPMorgan Chase \& Co.}
\descript{| Software Engineer Intern }
\location{June 2019 – August 2019 | Hong Kong}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Worked with Equities Prime brokerage team to create a client report-engine using \custombold{React.JS and Bottle.py}. Migrated the existing stack in \custombold{Java and C\#} to a web based platform in \custombold{Python and Typescript}.
\end{tightemize}
\begin{tightemize}\item Automated and Modularized the existing process ,reducing report generation and query execution time by over \custombold{35 \%}.
\end{tightemize}
\sectionsep
\runsubsection{FREEHUNTER}
\descript{| Software Developer }
\location{January 2019 – May 2019 | Hong Kong}
\begin{tightemize}\item Involved with the backend stack of web and mobile (React Native) platforms. Worked on \custombold{MERN (Mongo,Express,React and Node)} stack for developing web infrastructure of the company.
\end{tightemize}
\begin{tightemize}\item Deployed \custombold{EdgeRank} algorithm optimising the feeds by \custombold{40\%} and reducing feed loading time by \custombold{55\%}
\end{tightemize}
\sectionsep
\runsubsection{University College London}
\descript{| Summer Research Intern }
\location{June 2018 – August 2018 | London, UK | \href{https://github.com/abhimanyu891998/CS-Trackulum}{\custombold{Github Repo Link}}}
\begin{tightemize}\item Worked on project \custombold{”How are we teaching Computer Science?”}. Designed a database architecture in \custombold{mySQL} using \custombold{LAM} stack suitable for querying multiple data points related to CS curriculum of over 100 top universities.
\end{tightemize}
\begin{tightemize}\item Built a full stack web portal with \custombold{nodeJS,Express, EJS, MongoDB and mySQL} to directly interact,populate and query the database.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{PROJECTS AND ENTREPRENEURIAL WORKS}
\runsubsection{Clarifeye}
\descript{| HKD 100,000 SEED FUND}
Software for recruitment industry to simplify initial screening process
using a scoring based approach to predict the worthiness of an applicant
using Machine Learning. Used \custombold{SBS (Sequential Backward Selection)}
approach to identify most optimal features in a candidate’s application
and \custombold{SVM} for classifying candidates. 
\sectionsep
\\
\runsubsection{AssignTrack@HKU}
\descript{| Chrome Extension for HKU students with 470+ daily users | \href{https://github.com/abhimanyu891998/Assignment-Tracker-HKU}{\custombold{Github Repo Link}} }
Automatically reads assignment details from university portal and sorts
into a to-do list, helping students keep a track of assignments. Keeps a
track of submission status for every user and sorts assignments by
submission status. Extension added to \custombold{official HKU Portal}.
\sectionsep

\runsubsection{BIG TWO}
\descript{| Multiplayer Game in JAVA | \href{https://github.com/abhimanyu891998/Big-Two}{\custombold{Github Repo Link}}}
A full GUI enabled big two card game written in JAVA, supports multi player functionality by enabling socket networking and multi threading.\\
\sectionsep
\vspace{0.1 mm}

Full list of projects at \href{https://github.com/abhimanyu891998}{\custombold{github.com/abhimanyu891998}}
\vspace{1 mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{RELEVANT COURSEWORK}
\location{Computer Science:}
Data Structures & Algos (A) \textbullet{} Machine Learning (A+) \textbullet{} Operating Systems \textbullet{} Computer \& Commn Networks  \textbullet{}  OOP and Java (A-) \textbullet{} Software Engineering(A-) \\
\vspace{1 mm}
\location{Finance:}
Intro Micro \& Macro Economics \textbullet{}   Corporate Finance \textbullet{} Financial Accounting  
% \begin{tabular}{rll}
% % 2014	     & top 52/2500  & KPCB Engineering Fellow\\
% % % 2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
% % % 2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
% % % 2013	     & National  & Jump Trading Challenge Finalist\\
% % % 2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
% % % % 2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
% % % % 2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
% % % 2010     & National & Comp. Soc. of India's National Programming Contest\\
% % \end{tabular}

\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     SOCIETIES
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Societies} 

% \begin{tabular}{rll}
% 2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
% 2014   & National   & The Global Leadership and Education Forum (tGELF)\\
% 2012   &  National  & Golden Key International Honor Society\\
% 2012   &  National   & National Society of Collegiate Scholars\\
% \end{tabular}
% \sectionsep

\end{minipage} 
\end{document}